\documentclass{article}%

  % Document preamble.
  \usepackage{catchfile}%

  \newcommand{\getEnv}[2][]{%
    \CatchFileEdef%
      {\temp}%
      {"|kpsewhich --var-value #2 2>/dev/null"}{\endlinechar=-1}%
    \if%
      \relax%
      \detokenize{#1}
      \relax%
      \temp%
    \else%
      \let#1
      \temp%
    \fi%
  }%

  \newcommand{\echoValues}[2]{%
    \textbf{#1:}%
    \newline%
    [#2]%
  }%

  \getEnv[\texDist]{TEXMFDIST}%
  \getEnv[\wsl]{WSL_DISTRO_NAME}%
  \getEnv[\autodocPath]{AUTODOCPATH}%

% The document
\begin{document}%

\section{Greetings}
Hello \LaTeX!

\section{Commands \& Environment}\label{sec:side-effects}%
Confirm \textbf{echoValues} \& \textbf{getEnv} commands work.

\begin{itemize}%
  \item \echoValues{TEXMFDIST}{\texDist}%
  \item \echoValues{WSL\_DISTRO\_NAME}{\wsl}%
  \item \echoValues{AUTODOCPATH}{\autodocPath}%
\end{itemize}

\section{Installation Steps \& Side-effects}%
\begin{enumerate}%
  \item Ubuntu 20.04 installed into Windows Subsystem for Linux does not have
    graphical support.  miktex-console is not an option.

  \item TexLive was completely removed from Ubuntu 20.04 post installation

  \item MiKTeX Installation using ubuntu focal universe

  \begin{enumerate}%
    \item sudo apt-key adv --keyserver hkp://keyserver.ubuntu.com:80 --recv-keys D6BC243565B2087BC3F897C9277A7293F59E4889

    \item sudo apt-get update 

    \item sudo apt-get -y install miktex latexmk

    \item sudo miktexsetup --shared=yes finish was done

    \item sudo initexmf --admin --set-config-value [MPM]AutoInstall=1

    \item sudo mpm --admin --update
  \end{enumerate}%


  \item Post installation checks with this document.
  \begin{enumerate} 

    \item Document built with \textbf{kpsewhich} error.  Side-effects are
      seen in section \ref{sec:side-effects}.

    \item kpsewhich complains an MiKTeX administrator has not checked for
      updates.

    \item \textbf{kpsewhich --var-value HOME 2\>/dev/null} silences kpsewhich from
      the shell.  This is desired behavior.
  \end{enumerate}%


\item Questions
  \begin{enumerate} 

    \item How does one address: \textbf{major issue: So far, no MiKTeX
      administrator has checked for updates} without \textbf{miktex-console}?

    \item Why is \textbf{kpsewhich} reporting this error?


  \end{enumerate}%


\end{enumerate}%
\end{document}%
